\textbf{NBA Party}

### 2017-04-15 init_model.rnw
Added an SVM for its out of the box performance.

The data also contain information on the number of free throws, field goals, and
three pointers made and attempted by each player in each game.

@@

<<>>= 
musicians[, list(average.nmusicians = mean(nmusicians) %>% round(., digits = 1)),
          by = team][order(average.nmusicians)][c(1:5, 25:29)]
@

@@

>>>>

The minutes data also contain information on the number of free throws, field goals, and
three pointers made and attempted by each player in each game.

@@

<<echo=F>>= 
musicians[, list(average.nmusicians = mean(nmusicians) %>% round(., digits = 1)),
          by = team][order(average.nmusicians)][c(1:5, 25:29)]
@

@@

\paragraph{An out of the box machine learning model}
For fun, we try a simple support vector machine. We posit that whether
teams party also depends on how much time they have between games; even
when restricting our data to the twenty-four hour window after teams visit a party city, there is quite a bit of heterogeneity in when yesterday's game finished and when 
today's starts that a non-linear classifier may be able to take advantage of.

<<echo=2:5>>=
require(e1071)
svm.data <- lines[last.game.loc != team, list(hour = hour(date), last.game.time,
                                              party, season, outcome)] %>% na.omit

m <- svm(x = svm.data[season < 2016, -c('outcome', 'season'), with = F],
         y = svm.data[season < 2016, outcome == 'W'],
         scale = T, type = 'C-classification', probability = T, kernel = 'radial')

preds <- predict(m, newdata = svm.data[season == 2016, -c('outcome', 'season'), with = F])
table(preds, svm.data[season == 2016 , outcome])
@
